Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-22 docs/paper.tex
Vectorized counterexample ICT graphic

			\EndProcedure
		\end{algorithmic}
		\caption{Increasing Cost Tree Search}
		\label{icts-algo}
	\end{algorithm}
	\subsection{Exhaustive ICTS}
	\label{exhaustive}
	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals. Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible $m$. In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved. 
	\subsubsection{Bounded search}
	Once a solution is found for matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched. Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search. After solving each $m$ with solution cost $C_m$, let $B_{m+1} = \min(B_m,C_m)$. By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly. With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as	
	\[\Delta_{m,\text{bounded}} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,\text{bounded}}})$.
	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,\text{bounded}} = 0$.
	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,\text{bounded}}})$.
	\subsubsection{Ordered enumeration}
	\label{ordered-enum}
	To reduce the total effort, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$. In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}. This induces a case in which this enumeration minimizes the number of nodes searched in total (Property \ref{cond-monoton-optim}). However, cases in which $\Delta_m$ of the first $m$'s searched is much higher could also be constructed, in which case this approach might cause more nodes to be processed in total than alternative methods. Therefore, this ordered enumeration remains a heuristic improvement that works well in practice, as shown in Section \ref{experiments}.

>>>>

			\EndProcedure
		\end{algorithmic}
		\caption{Increasing Cost Tree Search}
		\label{icts-algo}
	\end{algorithm}
	\subsection{Exhaustive ICTS}
	\label{exhaustive}
	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals. Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible $m$. In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved. 
	\subsubsection{Bounded search}
	Once a solution is found for a 0-matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched. Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search. After solving each $m$ with solution cost $C_m$, let $B_{m+1} = \min(B_m,C_m)$. By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly. With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as	
	\[\Delta_{m,\text{bounded}} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,\text{bounded}}})$.
	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,\text{bounded}} = 0$.
	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,\text{bounded}}})$.
	\subsubsection{Ordered enumeration}
	\label{ordered-enum}
	To reduce the total effort, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$. In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}. This induces a case in which this enumeration minimizes the number of nodes searched in total (Property \ref{cond-monoton-optim}). However, cases in which $\Delta_m$ of the first $m$'s searched is much higher could also be constructed, in which case this approach might cause more nodes to be processed in total than alternative methods. Therefore, this ordered enumeration remains a heuristic improvement that works well in practice, as shown in Section \ref{experiments}.
